Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-07-23 analysis/report/effectiveness_report.Rmd
minor text edits

Comparative effectiveness will be estimated at weekly post-vaccination intervals to account for the potential differences in vaccine protection over time between the two brands.

Two time-scales are used for triagulation:

@@

* On the *treatment time-scale*, time zero is the date of vaccination. Calendar-time is included as an additional covariate, modelled as a restricted cubic spline.

@@

Note all counts below 6 are redacted.

>>>>

Comparative effectiveness is estimated at weekly post-vaccination intervals to account for the potential differences in vaccine protection over time between the two brands.

Two time-scales are used for triangulation:

@@

* On the *treatment time-scale*, time zero is the date of vaccination. Calendar-time is included as an additional covariate using restricted cubic spline with knots at the first and second tertile, plus boundary knots.

@@

Note all counts below 6 are redacted and Kaplan-Meier survival estimates are rounded for disclosure control.
